**Sequencing 16S rRNA gene fragments using the PacBio SMRT DNA sequencing system**

### 2016-01-06 Schloss_PacBio16S_PeerJ_2016.Rmd

**Figure 3. The relationship between the error rate of each region and the
composite quality scores for the sequences.** The error rates (A and C) and
percentage of sequences (B and D) were calculated for the reads that had a
composite quality score above the plotted value. The composite quality scores
were calculated by either determining the minimum value of the average quality
score wihin all 50-nt windows within each region (A and B) or by calculating
the average quality score across the entire sequence read (C and D).

>>>>

[ This figure removed ]
**Figure 3. The relationship between the error rate of each region and the
composite quality scores for the sequences.** The error rates (A and C) and
percentage of sequences (B and D) were calculated for the reads that had a
composite quality score above the plotted value. The composite quality scores
were calculated by either determining the minimum value of the average quality
score within all 50-nt windows within each region (A and B) or by calculating
the average quality score across the entire sequence read (C and D).
